Betting and Belief: Prediction Markets and Attribution of Climate Change

### 2016-03-27 prediction_market_wsc.Rnw
Fix a few typos.

\newcommand{Rstat}{\textsc{R}}

@@

Warming coefficients for each model were determined by linear regression of historical temperatures from 1880--2014 against the historical values for each model's forcing term. The noise model was determined by fitting an $\text{ARMA}(p,q)$ model to the residuals from the regression for all combinations of $p, q \in [0,1,2]$ and using the Watanabe-Akaike Information Criterion to select the optimal model \shortcite{Vehtari_2015}. This analysis was performed in \Rstat{} using the Stan probabilistic modeling language and the \texttt{rstan} package \shortcite{Stan2016,Rstan2016}. The optimal model in both cases was AR(1).

Future climates were generated by multiplying the warming coefficients for each model for warming coefficients adding stochastic AR(1) noise to deterministic warming using parameters fit to the historical data (1880--2014). One realization of future climates for both the $\ln(\ce{CO2})$ and TSI models is shown in Fig.~\ref{fig:climateplot}.

<<climateplot, eval=TRUE, echo=FALSE, message=FALSE, fig.cap="Historical measurements of temperature and temperature futures in two alternate realities.", fig.width=4, fig.height=3>>=
source("utils/climate_plot.R")
climate_plot() + theme(text=element_text(family='Palatino'))
@

\subsection{CLIMATE BELIEFS}

@@

\subsection{SOCIAL NETWORK}

Traders are part of a social network where each agent forms two links at random, and then forms links randomly, ensuring that each agent is connected to at least two other agents. 
Every time securities are realized, each trader looks at the performance of her richest neighbor in the network. 
Traders start with the same initial amount of ECU and differences in ECU can only come from market interactions.
Therefore, if some trader is poorer than her richest neighbor, the trader interprets it as a signal that her richest neighbor may have a better model of the climate.
Then, the trader considers adopting the model of her richest neighbor. 
For each trader, the willingness to revise her belief is determined by how ideologically loaded her belief is, which is a parameter we vary in our experiments.
\begin{figure}[t]
\begin{center}
\includegraphics[width=0.50\textwidth]{output/network.pdf}
\caption{An example of the social network among traders. Yellow circles indicate traders who believe that $\log\ce{CO2}$ is responsible for climate change and blue circles indicate traders who believe that TSI is responsible. Lines indicate social network connections.}\label{fig:social_network}%
\end{center}
\end{figure}

@@

At each time $t$, traders are assumed to know the past value of the temperature ${T}_{0:t}$, carbon dioxide $\text{CO2}_{0:t}$, and total solar irradiance $\text{TSI}_{0:t}$. 
In a sequence finishing at time $t^*$, traders also have common knowledge of $\text{CO2}_{t:t^*}$ and $\text{TSI}_{t:t^*}$, the future values of carbon dioxide and total solar irradiance up to $t^*$.
However, at any $t$, traders do not know the value of any future temperatures. 
In particular, in a given sequence, traders do not know the value of ${T}_{t^*}$. 
Traders can only predict ${T}_{t^*}$ using their approximate model and their knowledge of ${T}_{0:t}$, $\text{CO2}_{0:t^*}$, and $\text{TSI}_{0:t^*}$.
Notice that because ${T}_{0:t}$, $\text{CO2}_{0:t^*}$, and $\text{TSI}_{0:t^*}$ are common knowledge, in each period $t$, any two trader with the same approximate model $m$ forms the same stochastic beliefs about future temperatures $F_{tm}({T}_{t^*} ~|~ {T}_{0:t}, \text{CO2}_{0:t^*}, \text{TSI}_{0:t^*})$.

 At each time $t$, traders:

\begin{enumerate}
\item  recalibrate their approximate model based on the new set of temperature data available at $t$,
\item  compute their stochastic beliefs about future temperatures $F_{tm}({T}_{t^*} ~|~ {T}_{0:t}, \text{CO2}_{0:t^*}, \text{TSI}_{0:t^*})$ and use it to determine the expected value they attach to each security, and
\item  trade on the CDA market as follows: 
  \begin{itemize}
    \item Every trader $i$ choses at random a security $s_i^B$ she will try to buy.
    \item Every trader $i$ also chooses at random a security $s_i^S$ she will try to sell among the securities she owns a positive amount of (if any).
    \item Traders then decide of their selling price $p_i^S$ and buying price $p_i^B$. 
  To do so, traders first compute their expected values $E(s_i^B)$ and $E(s_i^S)$ for securities $s_i^B$ and $s_i^S$. 
  Then traders set $p_i^S$ at random above $E(s_i^S)$ and $p_i^B$ at random below $E(s_i^B)$ (see Model Parameters below for more details).

    \item Traders go to the market one at the time, in an order drawn randomly for each $t$.
    \item When trader $i$ comes to the market, she places limit orders in the order book. 
   These orders specify that $i$ is willing to buy $s_i^B$ at any price below $p_i^B$, and to sell $s_i^S$ at any price above $p_i^S$.
    \item The market maker then tries to match $i$'s orders with some order which was put in the book before $i$ came to the market.
    \item If there are  outstanding sell offers for $s_i^B$ at a price below $p_i^B$, a trade is concluded. 
   Trader $i$ buys one unit of $s_i^B$ from the sellers who sells at the lowest price below $p_i^B$, and the sell and buy offers are removed from the order book.
    \item If there are outstanding buy offers for $s_i^S$ at price above $p_i^S$, a trade is concluded. 
   Trader $i$ sells one unit to the buyer who buys at the highest price above $p_i^S$, and the sell and buy offers are removed from the order book.
    \item Whenever all traders have come to the market, any remaining outstanding offer is removed from the order book, and the trading period is concluded. 
  \end{itemize}
\end{enumerate}

@@

\subsection{MODEL PARAMETERS}

The model depends on the following parameters, which we vary in simulation experiments to determine their effects on the convergence of beliefs. We group the parameters into climate, network and individual behavioral factors.
\begin{itemize}
  \item Climate parameters:
  \begin{itemize}
    \item  extbf{true.model}: temperature data-generating process, \ce{CO2} or TSI.
  \end{itemize}
  \item Network parameters:
  \begin{itemize}
    \item  extbf{n.traders}: the number of traders.
    \item  extbf{n.edg}: the number of edges in the social network.
    \item  extbf{seg}: the initial degree of homophily in the network. The higher  extbf{seg}, the higher the initial homophily. 
  \end{itemize}

  \item Behavioral parameters:
  \begin{itemize}
    \item  extbf{risk.tak} : determines the distribution of risk-taking behavior. 
    For each trader $i$, the level of \texttt{risk.tak}$_i$ is drawn uniformly at random from $[0,$\texttt{risk.tak} $]$.
    The higher \texttt{risk.tak}$_i$, the higher (resp. lower) the price $i$ will set for the securities $i$ tries to sell (resp. buy).
    Formally, let $\texttt{reserv}_{it}$ be the reservation price of trader $i$ at time $t$ for some security $s$.
    Then trader $i$ picks her buying (resp. selling) price for $s$ uniformly at random in the interval  $[\texttt{reserv}_{it}, \allowbreak \texttt{reserv}_{it}  * (1 - \texttt{risk.tak}_i)]$ (resp. $[\texttt{reserv}_{it}, \allowbreak \texttt{reserv}_{it} * (1  + \texttt{risk.tak}_i)]$).

    \item  extbf{ideo} :  determines the degree of ``ideology'' of traders.
    For each trader $i$, the level of \texttt{ideo}$_i$ is drawn uniformly at random from $[0,$\texttt{ideo} $]$.
    If ideo is high, traders will not revise their approximate models easily, even when faced with evidence that their richest neighbor is doing better than them. 
    Formally, for each trader $i$ and each sequence, a parameter $d_{i}$ is drawn from $[0, \texttt{ideo}_i]$. 
    The value of $d_{i}$ is the probability that $i$ adopts the approximate model of her richest neighbor if that neighbor is doing better than $i$ at the end of the sequence (in monetary terms).
  \end{itemize}
\end{itemize}

@@

\subsection{FUTURE SCENARIOS}

Our primary focus is on simulating the market in future scenarios. This is more relevant for policy design and more interesting theoretically due to the increasing divergence of global temperature values under the two future scenarios. The sensitivity analysis is based on a Latin Hypercube Sampling of parameter sets from the following distributions \shortcite{beachkofski_improved_2002,carnell_lhs_2012}.

\begin{itemize}
  \item ideo $\sim Unif(0,1)$
  \item market.complet $\sim Unif(0,1000)$ (mapped into integer)
  \item n.edge $\sim Unif(100,200)$ (mapped into integer)
  \item n.traders $\sim Unif(50,250)$ (mapped into integer)
  \item risk.tak  $\sim Unif(0,1)$
  \item seg $\sim Unif(0,1)$
  \item true.model $\sim Binom(0.5)$
\end{itemize}

We use the model to simulate 10,000 outcomes based on the input paramter sets and then conduct a partial rank correlation coefficient analysis on the relationship between the input matrix, $X$, and the resulting simulated outcome vector of belief convergence scores, $y$ \shortcite{Marino2008,pujol_sensitivity:_2014,saltelli_sensitivity_2009}. Partial correlation computes the linear relationship between the part of the variation of $X_i$ and $y$ that are linearly independent of other $X_j$  ($j \neq i$).  The only difference with the partial correlation and the partial rank correlation that we use here is that the outcome variable $y$ is first ranked-transformed in order to allow us capture potentially non-linear relationships. That is every value, $y_s$, in the data set is replace by a number $f(y_s) \equiv |\{y_r~|~ y_s > y_r\}|$, where $y_r$ are the other observed values of $y$ in the data set.

Our sensitivity analysis, Fig.~\ref{fig:sa}, shows that ideology, risk tolerance, the number of traders, the number of edges per trader, the segmentation of the social network, and the true model all statistically significantly affect convergence. Segmented social networks can create an ``echo-chamber'' effect. Market participation causes traders to converge toward believing the ``true'' climate model; however, when the true model is \ce{CO2}-driven there is more convergence due to less noise in the relationship between predictor variable (log of \ce{CO2} versus TSI) and temperature.

<<sa, eval=TRUE, echo=FALSE, message=FALSE, fig.cap="Estimated effects of model parameters on convergence of beliefs in future scenario.", fig.width=3, fig.height=3.5>>=
# library(eat)
# load("output/src_future.Rda")
# plot(src_future, outcome_var = "Convergence") + theme_classic() + theme(text=element_text(family='Palatino'))

@@

The sensitivity analysis averages over time and thus masks time trends. We randomly drew from the above distributions for ideology, risk tolerance, and the number of traders, and conducted an experiment crossing 95% and 5% percentile values for the number of edges per trader and the segmentation of the social network and both values for the true model. We then collected the time series of convergence across these eight designs for visualization of the distributions of convergence over time (Fig.~\ref{fig:time}). Under most parameterizations, within 15-20 years, the median percent of traders believing in the true model is over 75%.

<<time, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Convergence over trading sequences.", fig.width=10.5, fig.height=8.5, fig.pos='t'>>=
source("utils/time_plot.R")
p1 <- history_box() + theme(text=element_text(family='Palatino'))
p2 <- future_box() + theme(text=element_text(family='Palatino'))
multi_plot(p1, p2, cols=2)
@

>>>>

\newcommand{\Rstat}{\textsf{R}}
\newcommand{\ARMA}{\text{ARMA}}
\newcommand{\AR}{\text{AR}}

@@

Warming coefficients for each model were determined by linear regression of historical temperatures from 1880--2014 against the historical values for each model's forcing term. The noise model was determined by fitting an $\ARMA(p,q)$ model to the residuals from the regression, using the \href{http://mc-stan.org}{Stan} probabilistic modeling language and the \href{https://cran.r-project.org/web/packages/rstan/}{\texttt{rstan}} package \shortcite{Stan2016,RStan2016}. We identified the optimal model for the autocorrelated noise term by perfroming the regression analysis for all combinations of $p, q \in [0,1,2]$ and using the Watanabe-Akaike Information Criterion to select the optimal noise model \shortcite{Vehtari_2015}. In both cases (TSI and $\log\ce{CO2}$), the optimal noise model was $\AR(1)$.

Future climates were generated by applying the warming coefficients to Eq.~\ref{eq:climate}:
\begin{equation}
T_{\text{model}}(t) = \beta_{\text{model}} F_{\text{model}}(t) + \varepsilon,
\label{eq:climate}
\end{equation}
where $T_{\text{model}}(t)$ is the temperature at time $t$, under a given model of what causes warming,
$F_{\text{model}}(t)$ is the forcing (TSI or $\log\ce{CO2}$) at time $t$,
$\beta_{\text{model}}$ is the regression coefficient, and
$\varepsilon$ is an $\ARMA(p,q)$ noise term.
The coefficient $\beta$ and the parameters of the ARMA noise model were fit to the historical data (1880--2014), as described above in Social Network.
An example realization of future climates for both the $\ln(\ce{CO2})$ and TSI models is shown in Fig.~\ref{fig:climateplot}.

<<climateplot, eval=TRUE, echo=FALSE, message=FALSE, fig.cap="Historical measurements of temperature and a realization of possible future temperatures under two alternate models of climate physics.", fig.width=4, fig.height=3>>=
source("utils/climate_plot.R")
climate_plot() + theme(text=element_text(family='Palatino'))
@

\subsection{Climate Beliefs}

@@

\subsection{Social Network}

Traders are part of a social network where each agent forms two links at random, and then forms links randomly, ensuring that each agent is connected to at least two other agents. 
Every time securities are realized, each trader looks at the performance of her richest neighbor in the network. 
Traders start with the same initial amount of ECU and differences in ECU can only come from market interactions.
Therefore, if some trader is poorer than her richest neighbor, the trader interprets it as a signal than her richest neighbor may have a better model of the climate.
Then, the trader considers adopting the model of her richest neighbor. 
For each trader, the willingness to revise her belief is determined by how ideologically loaded her belief is, which is a parameter we vary in our experiments.
\begin{figure}[t]
\begin{center}
\includegraphics[width=0.50\textwidth]{output/network.pdf}
\caption{An example of the social network among traders. Yellow and blue circles represent traders who believe in the two different models of climate change. Lines indicate social network connections. In a highly segmented network (\texttt{seg} close to 1), most links connect like-minded traders and few connect traders with opposing beliefs.}\label{fig:social_network}%
\end{center}
\end{figure}

@@

At each time $t$, traders are assumed to know the past value of the temperature ${T}_{0:t}$, carbon dioxide $\text{CO2}_{0:t}$, and total solar irradiance $\text{TSI}_{0:t}$. 
In a sequence finishing at time $t^*$, traders also have common knowledge of $\text{CO2}_{t:t^*}$ and $\text{TSI}_{t:t^*}$, the future values of carbon dioxide and total solar irradiance up to $t^*$.
However, at any $t$, traders do not know the value of any future temperatures. 
Thus, the traders know the forcing terms for the rest of the trading sequence, but do not know the value of ${T}_{t^*}$. 
Traders can only predict ${T}_{t^*}$ using their approximate model and their knowledge of ${T}_{0:t}$, $\text{CO2}_{0:t^*}$, and $\text{TSI}_{0:t^*}$.
Notice that because ${T}_{0:t}$, $\text{CO2}_{0:t^*}$, and $\text{TSI}_{0:t^*}$ are common knowledge, in each period $t$, any two trader with the same approximate model $m$ forms the same stochastic beliefs about future temperatures $P_{t,m}({T}_{t^*} ~|~ {T}_{0:t}, \text{CO2}_{0:t^*}, \text{TSI}_{0:t^*})$.
The probability distribution $P_{t,m}$ incorporates both epistemic uncertainty (the trader does not know the true values of the coefficients of the climate model) and aleatory uncertainty (in addition to deterministic warming, the temperature exhibits stochastic noise).

 At each time $t$, traders:
\begin{enumerate}
\item  recalibrate their approximate model based on the new set of temperature data available at $t$,
\label{step:calibrate}
\item  use the posterior probability distribution from (\ref{step:calibrate}) to 
assign beliefs about the probability distribution of future temperatures at time $t^*$: 
$P_{t,m}({T}_{t^*} ~|~ {T}_{0:t}, \text{CO2}_{0:t^*}, \text{TSI}_{0:t^*})$ 
and use it to determine the expected value they attach to each security, and
\item  trade on the CDA market as follows: 
  \begin{itemize}
    \item Every trader $i$ choses at random a security $s_i^B$ she will try to buy.
    \item Every trader $i$ also chooses at random a security $s_i^S$ she will try to sell among the securities she owns a positive amount of (if any).
    \item Traders then decide of their selling price $p_i^S$ and buying price $p_i^B$. 
  To do so, traders first compute their expected values $E(s_i^B)$ and $E(s_i^S)$ for securities $s_i^B$ and $s_i^S$. 
  Then traders set $p_i^S$ at random above $E(s_i^S)$ and $p_i^B$ at random below $E(s_i^B)$ (see Model Parameters below for more details).
    \item Traders go to the market one at the time, in an order drawn randomly for each $t$.
    \item When trader $i$ comes to the market, she places limit orders in the order book. 
   These orders specify that $i$ is willing to buy $s_i^B$ at any price below $p_i^B$, and to sell $s_i^S$ at any price above $p_i^S$.
    \item The market maker then tries to match $i$'s orders with some order which was put in the book before $i$ came to the market.
    \item If there are  outstanding sell offers for $s_i^B$ at a price below $p_i^B$, a trade is concluded. 
   Trader $i$ buys one unit of $s_i^B$ from the seller who sells at the lowest price below $p_i^B$, and the sell and buy offers are removed from the order book.
    \item If there are outstanding buy offers for $s_i^S$ at price above $p_i^S$, a trade is concluded. 
   Trader $i$ sells one unit to the buyer who buys at the highest price above $p_i^S$, and the sell and buy offers are removed from the order book.
    \item Whenever all traders have come to the market, any remaining outstanding offer is removed from the order book, and the trading period is concluded. 
  \end{itemize}
\end{enumerate}

@@

\subsection{Model Parameters}

The model depends on the following parameters, which we vary in simulation experiments to determine their effects on the convergence of beliefs. We group the parameters into climate, network and individual behavioral factors.
\begin{itemize}
  \item Climate parameters:
  \begin{itemize}
    \item  \texttt{true.model}: temperature data-generating process (\ce{CO2} or TSI).
  \end{itemize}
  \item Network parameters:
  \begin{itemize}
    \item  \texttt{n.traders}: the number of traders.
    \item  \texttt{n.edg}: the number of edges in the social network.
    \item  \texttt{seg}: the initial degree of homophily in the network. 
    The higher  \texttt{seg}, the higher the initial homophily. 
  \end{itemize}

  \item Behavioral parameters:
  \begin{itemize}
    \item  \texttt{risk.tak} : determines the distribution of risk tolerance with respect to successfully buying or selling securities.     Higher risk tolerance corresponds to demanding more aggressive prices for buying and selling, and hence, a higher risk of not consummating a trade that would be mutually advantageous to the buyer and seller.

    For each trader $i$, the level of $\texttt{risk.tak}_i$ is drawn uniformly at random from $[0,\texttt{risk.tak}]$.
    The higher $\texttt{risk.tak}_i$, the higher the price $i$ will demand for selling securities, and the lower the price $i$ will offer for buying.

    Formally, let $\texttt{reserv}_{i,t}$ be the reservation price of trader $i$ at time $t$ for some security $s$.
    Then trader $i$ picks her buying or selling price for $s$ uniformly at random in the interval  
    $[(1 - \texttt{risk.tak}_i) \texttt{reserv}_{i,t}, \allowbreak  \texttt{reserv}_{i,t}]$ for buying and 
    $[\texttt{reserv}_{i,t}, \allowbreak (1  + \texttt{risk.tak}_i) \texttt{reserv}_{i,t}]$ for selling. 
  \item  \texttt{ideo} :  determines the degree of ``ideology'' of traders.
    For each trader $i$, the level of $\texttt{ideo}_i$ is drawn uniformly at random from $[0,\texttt{ideo}]$.
    If \texttt{ideo} is high, traders will not revise their approximate models easily, even when faced with evidence that their richest neighbor is doing better than them. 
    Formally, for each trader $i$ and each sequence, a parameter $d_{i}$ is drawn from $[0, \texttt{ideo}_i]$. 
    The value of $d_{i}$ is the probability that $i$ adopts the approximate model of her richest neighbor if that neighbor is doing better than $i$ at the end of the sequence (in monetary terms).
  \end{itemize}
\end{itemize}

@@

\subsection{Future Scenarios}

Our primary focus is on simulating the market in future scenarios. This is more relevant for policy design and more interesting theoretically due to the increasing divergence of global temperature values under the two future scenarios. The sensitivity analysis is based on a Latin hypercube sampling of parameter sets from the following distributions \shortcite{beachkofski_improved_2002,carnell_lhs_2012}.

\begin{itemize}
  \item \texttt{ideo} $\sim \text{Uniform}(0,1)$
  \item \texttt{market.complet} $\sim \text{Uniform}(0,1000)$ (mapped into integer)
  \item \texttt{n.edge} $\sim \text{Uniform}(100,200)$ (mapped into integer)
  \item \texttt{n.traders} $\sim \text{Uniform}(50,250)$ (mapped into integer)
  \item \texttt{risk.tak}  $\sim \text{Uniform}(0,1)$
  \item \texttt{seg} $\sim \text{Uniform}(0,1)$
  \item \texttt{true.model} $\sim \text{Bernoulli}(0.5)$
\end{itemize}

The future \ce{CO2} forcing is taken from the RCP~8.5 scenario \shortcite{Riahi_2011} and the future TSI forcing is taken from a prediction of 21\textsuperscript{st} Total Solar Irradiance by \shortciteN{Velasco_Herrera_2015}. Because of the stochastic noise term, the temperature time series were different in each simulation.

We use the model to perform 10,000 simulations for each input paramter set, and then conducted a partial rank correlation coefficient analysis on the relationship between the input matrix, $X$, and the resulting simulated outcome vector of belief convergence scores, $y$ \shortcite{Marino2008,pujol_sensitivity:_2014,saltelli_sensitivity_2009}. Partial correlation computes the linear relationship between the part of the variation of $X_i$ and $y$ that are linearly independent of other $X_j$  ($j \neq i$).  The only difference between the partial correlation and the partial rank correlation that we use here is that the outcome variable $y$ is first ranked-transformed in order to allow us capture potentially non-linear relationships: every value, $y_s$, in the data set is replaced by a number 
$f(y_s) \equiv |\{y_r~|~ y_s > y_r\}|$, 
where $y_r$ are the observed values of $y$ in the data set.

<<sa, eval=TRUE, echo=FALSE, message=FALSE, fig.cap="Estimated effects of model parameters on convergence of beliefs in future scenario. Positive numbers accelerate convergence and negative numbers retard it. True model refers to the true climate model being \\ce{CO2}, so traders converge to the true model more quickly when carbon dioxide drives climate change than when total solar irradiance does. \\textbf{TODO: John: explain the error bars: one sigma, two sigma, 95\\% CI, \\dots}", fig.width=3, fig.height=3.5>>=
# library(eat)
# load("output/src_future.Rda")
# plot(src_future, outcome_var = "Convergence") + theme_classic() + theme(text=element_text(family='Palatino'))

@@

The sensitivity analysis averages over time and thus masks time trends. We randomly drew from the above distributions for ideology, risk tolerance, and the number of traders, and conducted an experiment crossing 95\textsuperscript{th} and 5\textsuperscript{th} percentile values for the number of edges per trader and the segmentation of the social network and both values for the true model. We then collected the time series of convergence across these eight designs for visualization of the distributions of convergence over time (Fig.~\ref{fig:time}). Under most parameterizations, within 15--20 years, the median fraction of traders believing in the true model is over 75\%.

<<time, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Convergence over trading sequences for different degrees of social-network connection and segmentation.", fig.width=10.5, fig.height=8.5, fig.pos='t'>>=
source("utils/time_plot.R")
p1 <- history_box() + theme(text=element_text(family='Palatino'))
p2 <- future_box() + theme(text=element_text(family='Palatino'))
multi_plot(p1, p2, cols=2)
@

### 2016-03-27 prediction_market_wsc.tex
Fix a few typos.

Future climates were generated by applying the warming coefficients to Eq.~\ref{eq:climate}:
\begin{equation}
T_{\text{model}}(t) = \beta_{\text{model}} F_{\text{model}}(t) + \varepsilon,
\label{eq:climate}
\end{equation}
where $T_{\text{model}}(t)$ is the temperature at time $t$, under a given model of what causes warming,
$F_{\text{model}}(t)$ is the forcing (TSI or $\log\ce{CO2}$) at time $t$,
$\beta_{\text{model}}$ is the regression coefficient, and
$\varepsilon$ is an $\ARMA(p,q)$ noise term.
The coefficient $\beta$ and the parameters of the ARMA noise model were fit to the historical data (1880--2014), as described above. 
An example realization of future climates for both the $\ln(\ce{CO2})$ and TSI models is shown in Fig.~\ref{fig:climateplot}.

@@

Traders are part of a social network where each agent forms two links at random, and then forms links randomly, ensuring that each agent is connected to at least two other agents. 
Every time securities are realized, each trader looks at the performance of her richest neighbor in the network. 
Traders start with the same initial amount of ECU and differences in ECU can only come from market interactions.
Therefore, if some trader is poorer than her richest neighbor, the trader interprets it as a signal that her richest neighbor may have a better model of the climate.
Then, the trader considers adopting the model of her richest neighbor. 
For each trader, the willingness to revise her belief is determined by how ideologically loaded her belief is, which is a parameter we vary in our experiments.
\begin{figure}[t]
\begin{center}
\includegraphics[width=0.50\textwidth]{output/network.pdf}
\caption{An example of the social network among traders. Yellow and blue circles represent traders who believe in the two different models of climate change. Lines indicate social network connections. In a highly segmented network (\texttt{seg} close to 1), most links connect like-minded traders and few connect traders with opposing beliefs.}\label{fig:social_network}%
\end{center}
\end{figure}

@@

 At each time $t$, traders:
\begin{enumerate}
\item  recalibrate their approximate model based on the new set of temperature data available at $t$,
\label{step:calibrate}
\item  use the posterior probability distribution from (\ref{step:calibrate}) to 
assign beliefs about the probability distribution of future temperatures at time $t^*$: 
$P_{t,m}({T}_{t^*} ~|~ {T}_{0:t}, \text{CO2}_{0:t^*}, \text{TSI}_{0:t^*})$ 
and use it to determine the expected value they attach to each security, and
\item  trade on the CDA market as follows: 
  \begin{itemize}
    \item Every trader $i$ choses at random a security $s_i^B$ she will try to buy.
    \item Every trader $i$ also chooses at random a security $s_i^S$ she will try to sell among the securities she owns a positive amount of (if any).
    \item Traders then decide of their selling price $p_i^S$ and buying price $p_i^B$. 
  To do so, traders first compute their expected values $E(s_i^B)$ and $E(s_i^S)$ for securities $s_i^B$ and $s_i^S$. 
  Then traders set $p_i^S$ at random above $E(s_i^S)$ and $p_i^B$ at random below $E(s_i^B)$ (see Model Parameters below for more details).
    \item Traders go to the market one at the time, in an order drawn randomly for each $t$.
    \item When trader $i$ comes to the market, she places limit orders in the order book. 
   These orders specify that $i$ is willing to buy $s_i^B$ at any price below $p_i^B$, and to sell $s_i^S$ at any price above $p_i^S$.
    \item The market maker then tries to match $i$'s orders with some order which was put in the book before $i$ came to the market.
    \item If there are  outstanding sell offers for $s_i^B$ at a price below $p_i^B$, a trade is concluded. 
   Trader $i$ buys one unit of $s_i^B$ from the sellers who sells at the lowest price below $p_i^B$, and the sell and buy offers are removed from the order book.
    \item If there are outstanding buy offers for $s_i^S$ at price above $p_i^S$, a trade is concluded. 
   Trader $i$ sells one unit to the buyer who buys at the highest price above $p_i^S$, and the sell and buy offers are removed from the order book.
    \item Whenever all traders have come to the market, any remaining outstanding offer is removed from the order book, and the trading period is concluded. 
  \end{itemize}
\end{enumerate}

@@

    Formally, let $\texttt{reserv}_{i,t}$ be the reservation price of trader $i$ at time $t$ for some security $s$.
    Then trader $i$ picks her buying or selling price for $s$ uniformly at random in the interval  
    $[(1 - \texttt{risk.tak}_i) \texttt{reserv}_{i,t}, \allowbreak  \texttt{reserv}_{i,t}]$ for buying and 
    $[\texttt{reserv}_{i,t}, \allowbreak (1  + \texttt{risk.tak}_i) \texttt{reserv}_{i,t}]$ for selling. 
  \item  \texttt{ideo} :  determines the degree of ``ideology'' of traders.
    For each trader $i$, the level of $\texttt{ideo}_i$ is drawn uniformly at random from $[0,\texttt{ideo}]$.
    If ideo is high, traders will not revise their approximate models easily, even when faced with evidence that their richest neighbor is doing better than them. 
    Formally, for each trader $i$ and each sequence, a parameter $d_{i}$ is drawn from $[0, \texttt{ideo}_i]$. 
    The value of $d_{i}$ is the probability that $i$ adopts the approximate model of her richest neighbor if that neighbor is doing better than $i$ at the end of the sequence (in monetary terms).
  \end{itemize}
\end{itemize}

>>>>

Future climates were generated by applying the warming coefficients to Eq.~\ref{eq:climate}:
\begin{equation}
T_{\text{model}}(t) = \beta_{\text{model}} F_{\text{model}}(t) + \varepsilon,
\label{eq:climate}
\end{equation}
where $T_{\text{model}}(t)$ is the temperature at time $t$, under a given model of what causes warming,
$F_{\text{model}}(t)$ is the forcing (TSI or $\log\ce{CO2}$) at time $t$,
$\beta_{\text{model}}$ is the regression coefficient, and
$\varepsilon$ is an $\ARMA(p,q)$ noise term.
The coefficient $\beta$ and the parameters of the ARMA noise model were fit to the historical data (1880--2014), as described above in Social Network.
An example realization of future climates for both the $\ln(\ce{CO2})$ and TSI models is shown in Fig.~\ref{fig:climateplot}.

@@

Traders are part of a social network where each agent forms two links at random, and then forms links randomly, ensuring that each agent is connected to at least two other agents. 
Every time securities are realized, each trader looks at the performance of her richest neighbor in the network. 
Traders start with the same initial amount of ECU and differences in ECU can only come from market interactions.
Therefore, if some trader is poorer than her richest neighbor, the trader interprets it as a signal than her richest neighbor may have a better model of the climate.
Then, the trader considers adopting the model of her richest neighbor. 
For each trader, the willingness to revise her belief is determined by how ideologically loaded her belief is, which is a parameter we vary in our experiments.
\begin{figure}[t]
\begin{center}
\includegraphics[width=0.50\textwidth]{output/network.pdf}
\caption{An example of the social network among traders. Yellow and blue circles represent traders who believe in the two different models of climate change. Lines indicate social network connections. In a highly segmented network (\texttt{seg} close to 1), most links connect like-minded traders and few connect traders with opposing beliefs.}\label{fig:social_network}%
\end{center}
\end{figure}

@@

 At each time $t$, traders:
\begin{enumerate}
\item  recalibrate their approximate model based on the new set of temperature data available at $t$,
\label{step:calibrate}
\item  use the posterior probability distribution from (\ref{step:calibrate}) to 
assign beliefs about the probability distribution of future temperatures at time $t^*$: 
$P_{t,m}({T}_{t^*} ~|~ {T}_{0:t}, \text{CO2}_{0:t^*}, \text{TSI}_{0:t^*})$ 
and use it to determine the expected value they attach to each security, and
\item  trade on the CDA market as follows: 
  \begin{itemize}
    \item Every trader $i$ choses at random a security $s_i^B$ she will try to buy.
    \item Every trader $i$ also chooses at random a security $s_i^S$ she will try to sell among the securities she owns a positive amount of (if any).
    \item Traders then decide of their selling price $p_i^S$ and buying price $p_i^B$. 
  To do so, traders first compute their expected values $E(s_i^B)$ and $E(s_i^S)$ for securities $s_i^B$ and $s_i^S$. 
  Then traders set $p_i^S$ at random above $E(s_i^S)$ and $p_i^B$ at random below $E(s_i^B)$ (see Model Parameters below for more details).
    \item Traders go to the market one at the time, in an order drawn randomly for each $t$.
    \item When trader $i$ comes to the market, she places limit orders in the order book. 
   These orders specify that $i$ is willing to buy $s_i^B$ at any price below $p_i^B$, and to sell $s_i^S$ at any price above $p_i^S$.
    \item The market maker then tries to match $i$'s orders with some order which was put in the book before $i$ came to the market.
    \item If there are  outstanding sell offers for $s_i^B$ at a price below $p_i^B$, a trade is concluded. 
   Trader $i$ buys one unit of $s_i^B$ from the seller who sells at the lowest price below $p_i^B$, and the sell and buy offers are removed from the order book.
    \item If there are outstanding buy offers for $s_i^S$ at price above $p_i^S$, a trade is concluded. 
   Trader $i$ sells one unit to the buyer who buys at the highest price above $p_i^S$, and the sell and buy offers are removed from the order book.
    \item Whenever all traders have come to the market, any remaining outstanding offer is removed from the order book, and the trading period is concluded. 
  \end{itemize}
\end{enumerate}

@@

    Formally, let $\texttt{reserv}_{i,t}$ be the reservation price of trader $i$ at time $t$ for some security $s$.
    Then trader $i$ picks her buying or selling price for $s$ uniformly at random in the interval  
    $[(1 - \texttt{risk.tak}_i) \texttt{reserv}_{i,t}, \allowbreak  \texttt{reserv}_{i,t}]$ for buying and 
    $[\texttt{reserv}_{i,t}, \allowbreak (1  + \texttt{risk.tak}_i) \texttt{reserv}_{i,t}]$ for selling. 
  \item  \texttt{ideo} :  determines the degree of ``ideology'' of traders.
    For each trader $i$, the level of $\texttt{ideo}_i$ is drawn uniformly at random from $[0,\texttt{ideo}]$.
    If \texttt{ideo} is high, traders will not revise their approximate models easily, even when faced with evidence that their richest neighbor is doing better than them. 
    Formally, for each trader $i$ and each sequence, a parameter $d_{i}$ is drawn from $[0, \texttt{ideo}_i]$. 
    The value of $d_{i}$ is the probability that $i$ adopts the approximate model of her richest neighbor if that neighbor is doing better than $i$ at the end of the sequence (in monetary terms).
  \end{itemize}
\end{itemize}
